Most discussions on China's debt trap have been so far limited to narrative statistics.
To objectively assess this issue, I adopt the up-to-date sovereign debt default model in the literature as a tool for empirical analysis. \citet{Na-18} propose a model to study the Argentine economy. \citet*{Hinrichsen_2020-chapter4} uses the model to evaluate the enforcement of sovereign debt under war reparations.
The model in my thesis strictly follows \citet{Na-18} and \citet*{Hinrichsen_2020-chapter4}.

International debt often lacks enforcement, and governments hold the decision of whether to repay the debt or default, based on the comparison of future values \citep*{Eaton-Gersovitz-81}. Therefore, default can be considered an optimal policy for a country that faces unsustainable debt levels. By defaulting, the country avoids the burden of paying interest on the debt, but it also faces the consequence of being excluded from the international credit market for a period of time. As a result, the country must rely solely on its own financial resources until it regains access to international credit markets.

Studies have pointed out that sovereign debt defaults are often accompanied by a devaluation of the currency. \citet*{Reinhart02} refers to this phenomenon as ``Twin Ds.''
Empirical analysis by \citet{Na-18} further presents that the devaluation rate often decreases after the time of default, suggesting that the Twin Ds phenomenon is the joint result of an optimal policy.
They proposed a model that incorporates two key frictions: limited commitment to repay external debts and downward nominal wage rigidity.
It is a decentralized version of the Eaton-Gersovitz sovereign debt model.
The model predicts that default will occur only after a series of increasingly negative output shocks. Prior to default, domestic absorption experiences a severe contraction, which leads to a decline in labor demand. Nevertheless, since the nominal wage has a downward rigidity that limits the adjustment, real wages fail to adjust downward, causing involuntary unemployment to occur. To prevent this, the government's optimal policy is to devalue the domestic currency, thereby reducing the real value of wages. Default episodes are hence usually accompanied by significant currency devaluations in both the model and the data \citep{Na-18}.

For the sovereign debt model, I closely follow \citet{Na-18} to examine the set of conditions under which default is the optimal decision.
The calibrated model will then serve as a benchmark metric for investigating whether China has potentially trapped heavily indebted poor counties into default, using the approach proposed by \citet*{Hinrichsen_2020-chapter4}.

\section{Households}
\input{sections/model-sec/hh.tex}

\section{Firms}
\input{sections/model-sec/firm.tex}

\section{Downward Nominal Wage Rigidity}
\input{sections/model-sec/rigid.tex}

\section{Government}
\input{sections/model-sec/gov.tex}

\section{Foreign Lenders}
\input{sections/model-sec/lender.tex}

\section{Competitive Equilibrium}
\input{sections/model-sec/CE.tex}

\section{Default Decision}
\label{sec: model-default-decision}
\input{sections/model-sec/default.tex}

