Following the standard Eaton-Gersovitz framework, this study's model considers the following three value functions:
value of continuing to repay the debt $v^c$, value of being in good standing $v^g$, and value of being in bad standing $v^b$.

Under the period of being in good financial standing, the value for the government to continue repaying the debt is the maximum value of the utility gained by the households this period, plus the discounted value of being in a good financial standing, subject to the households' budget constraints. Formally, this appears as:
\begin{equation}
    \label{eq:vc}
    \begin{aligned}
        v^c(y^T_t, d_t) = \max_{\left\{ c^T_t, h_t, d_{t+1} \right\}} \quad
        &\left\{
            U\left(
                A\left(c^T_t, F(h_t)\right)
             \right)
             + \beta E_t
             v^g \left(
                y^T_{t+1}, d_{t+1}
              \right)
         \right\}\\
          \text{s.t} \quad& c^T_t + d_t = y^T_t + q(y^T_t, d_{t+1}) d_{t+1} \\
                    & h_t \le \bar{h}.
    \end{aligned}
\end{equation}
Here, the first constraint is obtained by setting $I_t = 1$ in \refeq{eq:market-clearing}, and the second constraint is on working hours.

If the country is in bad standing, then its consumption of tradable goods experiences a loss. The government has probability $\theta$ of regaining access to international financial markets, and probability $1 - \theta$ of continuing in bad standing. During the period in bad standing, the country obtains no international borrowing, and so the state variable for debt is excluded. Formally, this implies:
\begin{equation}
    \label{eq:vb}
    \begin{aligned}
        v^b(y^T_t) = \max_{\left\{ h_t \right\}} \quad
        &\left\{
            U\left(
                A\left( y^T_t - L(y^T_t), F(h_t)\right)
             \right)
             + \beta E_t \left[
                \theta v^g \left(
                    y^T_{t+1}, 0
                \right)
                + (1-\theta) v^b \left(
                    y^{T}_{t+1}
                 \right)
            \right]
         \right\}\\
          \text{s.t} \quad& h_t \le \bar{h}.
    \end{aligned}
\end{equation}
The tradable consumption $c^T_t = y^T_t - L(y^T_t)$ again follows \refeq{eq:market-clearing} by setting $I_t = 0$, and it is substituted explicitly into the value function.

If the country is in good standing, then the government has the freedom to choose which is best for it to do: to continue paying its debt or to default. The decision is made by comparing the value functions of the two scenarios, given the current output shock for tradable goods and the current level of debt:
\begin{equation}
    \label{eq:vg}
    v^g(y^T_t, d_t) = \max\left\{
        v^c(y^T_t, d_t) ,
        v^b(y^T_t)
     \right\}.
\end{equation}

Define the default set $D(d_t)$ as the set of tradable-output levels $y^T_t$ examined by the government in period $t$, in which the government's optimal respond is to default.
It is formally presented as:
\begin{equation}
    \label{eq:default-set}
    D(d_t) = \left\{ 
        y^T_t : v^b(y^T_t) > v^c(y^T_t, d_t)
     \right\}.
\end{equation}
In other words, given a current debt level $d_t$, if the government observes that $y^T_t$ is inside $D(d_t)$, then it chooses to default.

Under rational expectations, foreign lenders recognize the default set, and hence the price for debt is determined by Equation \eqref{eq:lender}, given by:
\begin{equation}
    q(y^T_t, d_{t+1}) =
    \frac{1 - \Pr\left\{ y^T_{t+1} \in D(d_{t+1}) \mid y^T_t \right\}}{1 + r^*}.
\end{equation}
Note that the price of debt enters the value function of continuing paying its debts, $v^c(y^T_t, d_{t})$.

It is obvious that the optimal labor supply is $h_t = \bar{h}$ since all functions, $F, A, \text{and} U$, are monotonic, implying under the freedom to choose the devaluation rate and the tax on debt, the government can ensure full employment. Denote $w^f(c^T_t)$ as the equilibrium wage function under full employment given the consumption of tradable goods. Combining Equation \eqref{eq:firm-FOC} and the Euler equation in \eqref{eq:FOC-HH-1} and imposing the optimal policy $h_t = \bar{h}$ lead to:
\begin{equation}
    w_t = w^f(c^T_t) \equiv \frac{A_2(c^T_t, F(\bar{h}))}{A_1(c^T_t, F(\bar{h}))} F'(\bar{h}).
\end{equation}

Knowing that the wage has downward nominal rigidity, the government sets the devaluation rate accordingly. Downward rigidity \eqref{eq:wage-rigid} states that:
\begin{equation*}
    \gamma \le \frac{W_t}{W_{t-1}} = \frac{w_t}{w_{t-1}} \frac{P^T_t}{P^T_{t-1}} = \epsilon \frac{w_t}{w_{t-1}},
\end{equation*}
where the second equal sign comes from Equation \eqref{eq:devaluation-rate}. Substituting the wage under full employment gives:
\begin{equation}
    \epsilon_t \ge \gamma \frac{w_{t-1}}{w^f(c^T_t)}.
\end{equation}
This is the family of optimal devaluation policies. Following \citet{Na-18} and \citet*{Hinrichsen_2020-chapter4}, I assume that the government chooses the minimal devaluation target that stabilizes nominal wages -- that is, $
    \epsilon_t = \gamma \frac{w_{t-1}}{w^f(c^T_t)}.
$

The optimal devaluation policy is designed to maintain the equilibrium real wage at the level of full-employment real wage consistently, thereby addressing the distortions caused by nominal rigidities. The tax policy, on the other hand, focuses on resolving the borrowing externality by ensuring that the household's Euler equation \eqref{eq:FOC-HH-3} is satisfied.%
\footnote{
    In other words, tax in this model is not used as a channel for the government to repay debt, but as a channel to undo the distortions.
}
The probability of default is thus considered by the household through the tax policy.