The value function iteration of the model depends on the persistency and volatility of the AR(1) process for the tradable output, namely $(\rho, \sigma_u)$. The parameters are obtained with the cyclical component after conducting the HP-filter. In addition, the x-coordinate of the data points plotted on the default set is also obtained with the cyclical component, representing the deviation from the trend. One may concern that the method of detrending might yield a different conclusion. In \citet{Na-18} and \cite{Hinrichsen_2020-chapter4}, the output process is detrended using the log-quadratic filter\footnote{
    In specific, assume that the real GDP can be expressed by the cyclical component and trend (secular) component $y_t = y^s_t + y^c_t$. The components are then estimated by running the OLS: $y_t = a + bt + ct^2 + \epsilon_t$, then set $y^c_t = \epsilon_t$ and $y^s_t = a + bt + ct^2$ \citep{Uribe-Schmitt-Grohe-textbook}.
}. Generally, the volatility for the cyclical component obtained with log-quadratic filter is higher than that of HP-filter \citep{Uribe-Schmitt-Grohe-textbook}.

Figure~\ref{fig:decompose-trad-logq} illustrates the decomposition of the (per capita) tradable output using the log-quadratic filter. It yields $(\rho, \sigma_u)=$ (0.9325, 0.0266) for Sri Lanka and $(\rho, \sigma_u)=$ (0.9239, 0.0174) for Pakistan. Compared to the unconditional standard deviation of 4.37\% for Sri Lanka's per capita tradable output using the HP-filter, the log-quadratic filter yields 7.38\%; similarly, the unconditional standard deviation for Pakistan's per capita tradable output using the HP-filter is 2.21\%, while the log-quadratic filter yields 4.55\%.
See Table~\ref{tab:ar1-filter} for the comparison.

The default set and the corresponding debt-output pairs when the output process is obtained via log-quadratic filter is shown in Figure~\ref{fig: ds-logq}. Interestingly, the number of years when Sri Lanka was within the default set reduces, as depicted in Figure~\ref{fig: ds-sri-logq}.
In contrast to the results obtained with the HP-filter, the year 2009 is now considered safe, albeit on the verge of default. The remaining two years within the default set are 2015 and 2016, coinciding with the period when the newly elected president expressed his determination to alleviate Sri Lanka's burden of debt to China. These findings regarding the predicament faced by the new government remains robust when using the log-quadratic filter.
As for the case of Pakistan, the year 2017 is no longer under the default set, contrary to the result obtained with the HP-filter. Nevertheless, the trend of the debt-to-tradable-ratio kept increasing, and during the year 2017, the output deviated towards the positive direction ($y^T_t > 1$). If the output shock were to contract just by a mere 1\% (at $y^T_t = 0.99$), Pakistan would be falling into the default set.